---
title: "Class15"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## RStudio session alongside RNA-Seq demonstration


We downloaded Genotype Data from ENSEMBLE on the MXL Mexican ancestry in LA Dataset.

```{r}

mxl<-read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")

head(mxl)
```

What Proportion of this data are G/G etc?

We want to look at the second colmun that contains the genotype information.
```{r}
table(mxl[,2])
```

## RNA-Seq result analysis for different genotypes of this SNP

```{r}
expr<-read.table("rs8067378_ENSG00000172057.6.txt")
head(expr)
```

```{r}
AA<-which(expr$geno=="A/A")
mean(expr[AA,"exp"])
AAexp<-expr[expr$geno=="A/A", ]$exp

AG<-which(expr$geno=="A/G")
mean(expr[AG,"exp"])
AGexp<-expr[expr$geno=="A/G", ]$exp

GG<-which(expr$geno=="G/G")
mean(expr[GG,"exp"])
GGexp<-expr[expr$geno=="G/G", ]$exp

hist(AAexp)
```

## How do we plot a useful plot

Try a Box PLot

We will use the 'boxplot()' function

```{r}

boxplot(ex)


```