---
title: "Class14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## RNA-Seq analysis

```{r}
counts <- read.csv("airway_scaledcounts.csv", stringsAsFactors = FALSE)
metadata <-  read.csv("airway_metadata.csv", stringsAsFactors = FALSE)
head(counts)
head(metadata)
```

## We will compare treated versus control data based on counts on counts files
Have to use the metadata to determine what is treated vs what is control

```{r}
#metadata
#metadata$dex == "control"
control <- metadata[metadata$dex=="control",]
##taking metadata - only want rows where dex="control, so this gives us a data frame with just the control data. Adding the $id takes the id column of each of these

control
```

```{r}
# access the count columns with control$id

counts[, control$id]
##same as taking "counts[,c(2,4,6,8)]"
```

```{r}
# Now find the mean value for each gene (i.e. each row)
control.mean <- rowMeans(counts[, control$id])
names(control.mean) <- counts$ensgene
```

##Repeat for Treated

```{r}
treated <- metadata[metadata$dex=="treated",]
treated.mean <- rowMeans(counts[, treated$id])
names(treated.mean) <- counts$ensgene
```

```{r}
mycounts <- data.frame(control.mean, treated.mean)
mycounts

```
#plotting the data

```{r}
plot(mycounts)
```

```{r}
hist(mycounts$control.mean, breaks = 300)
```

```{r}
plot(mycounts, log="xy")
```
## Removing Zero count genes because we can't say anything about them from this dataset(!)
#Example of how this works

```{r}
x <- data.frame( c(1, 3, 10, 0),
                 c(1, 3, 0,  0) )

unique(which(x == 0, arr.ind = TRUE)[,"row"])
```

How to do this with my counts
```{r}

to.rm<- unique(which(mycounts == 0, arr.ind = TRUE)[,"row"])
newcounts<- mycounts[-to.rm,]
```

##Now we are down to 21817 obs

# Here we calculate log2foldchange, add it to out meancounts dataframe and inspect results either with the head() or te View() function for example

```{r}
newcounts$log2fc<- log2(newcounts[,"treated.mean"]/newcounts[,"control.mean"])
head(newcounts)

upregulated.genes<-length(which(newcounts$log2fc>2))
downregulated.genes <- length(which(newcounts$log2fc< -2))

upregulated.genes+downregulated.genes

```

##Time for DESeq2

```{r}
library(DESeq2)
```
#Setup the Object Required by Deseq
```{r}
dds <- DESeqDataSetFromMatrix(countData=counts, 
                              colData=metadata, 
                              design=~dex, 
                              tidy=TRUE)
dds

```

```{r}
dds <- DESeq(dds)
```
```{r}
res <- results(dds)
res
```

plot the data

```{r}
plot(res$log2FoldChange, -log(res$padj), col="gray")
abline(v=c(-2,+2), lty=2, col="red")
abline(h=-log(0.05), col= "blue")
```