---
title: "Analysis of the 2019-nCov Outbreak"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv

```{r}
virus <- read.csv("coronavirus_dataset.csv")

tail(virus)
```

Q1. How many total infected cases are there around the world?

```{r}
A1<-sum(virus$cases)
print(A1)
```
Q2. How many deaths linked to infected cases have there been

```{r}
A2<-sum(virus$cases[virus$type=="death"])
print(A2)
```
Q3. What is the overall death rate?

```{r}
A3<-100*A2/A1
```

Q4. What is the death rate in China?

```{r}
CasesinChina<- sum(virus$cases[virus$Country.Region=="Mainland China"])
DeathsinChina<- sum(virus$cases[virus$Country.Region=="Mainland China"&virus$type=="death"])
A4<-100*DeathsinChina/CasesinChina
A4
```
Q5. What is the death rate in Italy, Iran, and the US?



```{r}
CasesinItaly<- sum(virus$cases[virus$Country.Region=="Italy"])
DeathsinItaly<- sum(virus$cases[virus$Country.Region=="Italy"&virus$type=="death"])
A5.Italy<-100*DeathsinItaly/CasesinItaly


CasesinIran<- sum(virus$cases[virus$Country.Region=="Iran"])
DeathsinIran<- sum(virus$cases[virus$Country.Region=="Iran"&virus$type=="death"])
A5.Iran<-100*DeathsinIran/CasesinIran


CasesinUS<- sum(virus$cases[virus$Country.Region=="US"])
DeathsinUS<- sum(virus$cases[virus$Country.Region=="US"&virus$type=="death"])
A5.US<-100*DeathsinUS/CasesinUS


print(A5.Iran)
print(A5.Italy)
print(A5.US)
```

