---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(bio3d)
hsg_pdb<-get.pdb("1hsg")
```

```{r}
Hiv_prot<- read.pdb("1hsg.pdb")

Hiv_prot

```

##Q1: What is the name of the two non protein resid values in this structure? What does resid
correspond to and how would you get a listing of all reside values in this structure? 
A: HOH and MK1 and residue is the amino acids and you can get these values by listing or creating a vector of the atoms-Resid list

##Make ligand only ad prot only PDB Files

```{r}
prot <- atom.select(Hiv_prot, "protein", value=TRUE)
lig <- atom.select(Hiv_prot, "ligand", value=TRUE)
write.pdb(prot, file="1hsg_protein.pdb")
write.pdb(lig, file="1hsg_ligand.pdb")
```


## Loading in and inspecting Docking Results
```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
rmsd(atom.select(ori,"noh",value=TRUE),atom.select(res,"noh",value=TRUE))
```
##Normal Mode Analysis of protein structure
```{r}
library(bio3d)
pdb <- read.pdb("1HEL")
modes <- nma(pdb)
plot(modes, sse=pdb)
# Visualize NMA results
mktrj(modes, mode=7, file="nma_7.pdb")
```

