---
title: "Class10"
author: "Brandon Jones"
date: "2/7/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Get our input data

Our data for today come from the Wisconsin Breast Cancer Diagnostic Data Set

```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
head(wisc.df)
```

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```

> Q. How many patients are there in this dataset?

```{r}
nrow(wisc.df)
```

> Q. How many cancer and non-cancer patients are there?

```{r}
table(wisc.df$diagnosis)
```

```{r}
sum(wisc.df$diagnosis == "M")
```

> Q. How many cols are "_mean" values?

```{r}
colnames(wisc.df)
```

We can use the `grep()` function to see this

```{r}
grep("_mean", colnames(wisc.df), value=TRUE )
```

We can take the `length()` of this to find how many matches there are
```{r}
length( grep("_mean", colnames(wisc.df)) )
```


## Enter Principal Component Analysis

First we need to check whether our input data should be scaled. Lets check the sd() and mean() of all our columns in `wisc.data`

```{r}
round( apply(wisc.data, 2, sd), 2)
```

```{r}
# Perform PCA on wisc.data by completing the following code
wisc.pr <- prcomp( wisc.data, scale=TRUE )
summary(wisc.pr)
```

```{r}
biplot(wisc.pr)
```

This is a hot mess! We need to cook our own PCA plot. To do this we need to access the results within the wisc.pr project

```{r}
attributes(wisc.pr)
```

We want the $x component to make our PCA plot!
```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
```


Hierach Clustering

```{r}
plot(hclust((dist(wisc.data))))

wisc.data.scaled<-scale(wisc.data)

wisc.scaled.dist<-((dist(wisc.data.scaled)))

wisc.hclust<-hclust(wisc.scaled.dist)

plot(wisc.hclust)

wisc.cut<-cutree(wisc.hclust,k=4)
wisc.cut



table(wisc.cut, wisc.df$diagnosis)
```
I can cluster in PC space - in other words use the results of PCA to do my clustering


```{r}
wisc.pr.hc <- hclust( dist(wisc.pr$x[,1:3]), method="ward.D2" )
plot(wisc.pr.hc)
```

```{r}
grps <- cutree(wisc.pr.hc, k=2)
table(grps)
```

```{r}
table(grps, wisc.df$diagnosis)
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grps)
```


## Predicting

```{r}
#url <- "new_samples.csv"
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc

plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col="blue", pch=16, cex=3)
text(npc[,1], npc[,2], labels=c(1,2) , col="white")
```

